---
title:     'MMP and the Weather'
author:    "Facundo Danza & Eungik Lee"
susbtitle: "Descripitives, Plots, and Regressions"
---

# Pre-analysis

First, we clean the R-environment:
```{r}
rm(list = ls())
gc()
```

Second, we load (and install) the needed packages:
```{r}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(tidyverse, data.table, janitor, dplyr, fixest, 
               expss, ggpubr, xtable, scales, Hmisc)
```

Third, we define the `theme_set`:
```{r}
theme_set(theme_bw())
```

Lastly, we set the working directories:
```{r}
dir                     <- list()
dir$root                <- dirname(getwd())
dir$data                <- paste0(dirname(getwd()), "/data/")
dir$weather             <- paste0(dirname(getwd()),
                                  "/data/confidential/meteoblue/")
dir$results             <- paste0(dirname(getwd()), "/tables/")
dir$constructed_conf    <- paste0(dirname(getwd()),
                                  "/data/confidential/constructed/")
dir$constructed_data    <- paste0(dirname(getwd()),
                                  "/data/constructed/")

dir$fig                 <- paste0(dirname(getwd()), "/figures/")
```


# Meteoblue - Weather Data

## Load the data

First, we load the daily weather data (and drop the missing values of it):
```{r}
weather_daily = read.csv(paste0(dir$weather, "weather.csv")) %>%
              filter(!is.na(day))
```

Since our data is annual rather than daily, we take the average (or sum) of each variable. Furthermore, we only keep the months from April to September, the wet season in Mexico:
```{r}
month_start = 4
month_end   = 9

weather_year = weather_daily %>% 
  filter(month >= month_start & month <= month_end) %>%
  group_by(commun, year, month) %>%
  summarise(prec_m_sum=sum(precipitation),
            across(starts_with("temp"), mean)) %>%
  group_by(commun, year) %>%
  summarise(prec_y_mean=mean(prec_m_sum),
            across(starts_with("temp"), 
                   mean, .names = "{.col}_y_mean"))
```


```{r}
rm(weather_daily)
```


# Mexican Migration Project (MMP)

## Load the data

First, we load the data on MMP. We have already cleaned the data (you can find such code as "1.1_mmp_data_analysis.Rmd.")
```{r}
mmp = read.csv(paste0(dir$constructed_conf,
                      "mmp_individual_clean.csv")) %>% 
  filter(pop_2010 <= 100000) # keep only up to mid-size towns
```


# Merge MMP and Weather

We, then, merge data on weather with MMP, and keep only the communities with weather data:
```{r}
mmp_com_weather = left_join(mmp, 
                            weather_year, by = c("commun","year")) %>%
  filter(!is.na(prec_y_mean))
```


## Standarized Weather

First, we need to "standardized" our weather data; that is, we find the historical average and standard deviation over the period 1985-2019:
```{r}
start_yr_hist = 1985
end_yr_hist   = 2019

weather_norm = weather_year %>%
  filter(year <= end_yr_hist & 
           year >= start_yr_hist) %>%
  group_by(commun) %>%
  summarise(across(ends_with("y_mean"),
                   mean, .names = "{.col}_hist"),
              across(ends_with("y_mean"),
                   sd, .names = "{.col}_sd_hist"))
```

We add this "historical" dataset to the pre-existing one. 
```{r}
mmp_com_weather = left_join(mmp_com_weather, 
                            weather_norm, by = "commun")
```

```{r}
rm(weather_norm)
```

We only keep 10-year windows backwards (we include the 11 year for the regressions and plots we'll run later):
```{r}
year_window = 11

mmp_com_weather = mmp_com_weather %>% 
  filter((surveyyr - year) <= year_window)
```

We then proceed by taking the z-score for each weather variable. Specifically:
```{r}
mmp_com_weather = 
  mmp_com_weather %>% 
  mutate(prec_y_mean_dev = 
           (prec_y_mean - prec_y_mean_hist)/prec_y_mean_sd_hist, 
         temp_avg_y_mean_dev = 
           (temp_avg_y_mean - temp_avg_y_mean_hist)/temp_avg_y_mean_sd_hist, 
         temp_max_y_mean_dev = 
           (temp_max_y_mean - temp_max_y_mean_hist)/temp_max_y_mean_sd_hist, 
         temp_min_y_mean_dev = 
           (temp_min_y_mean - temp_min_y_mean_hist)/temp_min_y_mean_sd_hist)
```

We also take lag variables, which we believe is the relevant timing for the migration decision:
```{r}
mmp_com_weather = mmp_com_weather %>%
  filter(year >= 1989) %>%
  arrange(id, year)

mmp_com_weather = mmp_com_weather %>%
  group_by(id) %>%
  mutate(prec_y_mean_dev_lag = lag(prec_y_mean_dev),
         across(starts_with("temp") & ends_with("y_mean_dev"), ~ lag(.x),
                .names = "{.col}_lag")) %>% ungroup()
```


# Descriptives

In this section, we add the summary statistics of the model. Formally, we are only using the 10 year-backward window in our main analysis; we thus cut the data slightly:
```{r}
year_window = 10

mmp_com_weather_stats = mmp_com_weather %>% 
  filter((surveyyr - year) <= year_window)
```

We count the number of communities:
```{r}
n_com = mmp_com_weather_stats %>%
  group_by(commun) %>% summarise(n_obs = n()) %>% nrow()

n_com
```

We then create the first descripitve table. For some of the variable of interest, we take the average, the standard deviation, the minimum and the maximum. 
```{r}
table1 = mmp_com_weather_stats %>% 
  dplyr::summarise_at(.vars = "age", 
               .funs = c("Mean" = ~wtd.mean(.x, weights = weight),
                         "SD" = ~ sqrt(wtd.var(.x, weights = weight)),
                         "Min" = min,"Max" = max), 
               na.rm = T) 
# Fortunately, there are no missing values in our sample
table1 = cbind(Variable = "Age", table1)

var_names  = c("Male", "Educ. Level (Yr)","Agricultural Worker", 
               "Land Owner", "Business Owner","Owner", "Migrate*", 
               "Legally Migrate*", "Illegaly Migrate*")
i = 0
for (var in c("male", "educ_miss", 
              "ag_work", "land_owner", "business_owner", "owner", "M_U",
              "M_UL", "M_UIL")) {
  table_round = mmp_com_weather_stats %>% 
  summarise_at(.vars = var, 
               .funs = c("Mean" = ~wtd.mean(.x, weights = weight),
                         "SD" = ~ sqrt(wtd.var(.x, weights = weight)),
                         "Min" = min,"Max" = max), 
               na.rm = T) 

 i = i + 1
 table_round = cbind(Variable = var_names[i], table_round) 
 
 table1 = rbind(table1, table_round)
}


mmp_com_weather_stay = mmp_com_weather_stats %>% 
  group_by(id) %>% 
  summarise(n_trip  = sum(M_U, na.rm = T), 
            usdur_tot = sum(usdur, na.rm = T), 
            weight = mean(weight)) %>%
  mutate(us_exp_avg = ifelse(n_trip > 0 & usdur_tot > 0, 
                             (usdur_tot/n_trip), NA)) %>%
  filter(!is.na(us_exp_avg))

table_round = mmp_com_weather_stay %>% 
  summarise_at(.vars = "us_exp_avg", 
               .funs = c("Mean" = ~wtd.mean(.x, weights = weight),
                         "SD" = ~ sqrt(wtd.var(.x, weights = weight)),
                         "Min" = min,"Max" = max), 
               na.rm = T) 
table_round = cbind(Variable = "Length Stayed** (Mh)", table_round) 
 
table1 = rbind(table1, table_round)

table1 = table1 %>%
  mutate(across("Mean":"SD", ~ scales::comma(.x,
                                              accuracy = 0.001)),
         across("Max":"Min", ~ scales::comma(.x,
                                              accuracy = 1)))

n_ind = mmp_com_weather_stats %>%
  group_by(id) %>% summarise(n_obs = n()) %>% nrow()

n_ind = as.data.frame(cbind("Individuals", t(rep(n_ind, 4)))) %>%
  set_names(c("Variable", "Mean", "SD", "Min", "Max")) %>%
  mutate(across("Mean":"Max", ~ scales::comma(as.numeric(.x),
                                            accuracy = 1)))
  
n_obs = mmp_com_weather_stats %>% 
  summarise("Mean" = n(),"SD" = n(),"Min" = n(),"Max" = n()) 
  

n_obs = cbind(Variable = "Observations", n_obs) %>% 
  mutate(across("Mean":"Max", ~ scales::comma(.x,
                                              accuracy =1)))

table1 = rbind(table1, n_ind, n_obs)

table1
```

We save the table in latex's form:
```{r}
tab1 =xtable(table1, 
       caption = "Summary Statistics",
       align   = c("l","l","c","c","c","c"),
       label   = "desc_stats")

double_line = nrow(table1) - 2
print(tab1,file=paste0(dir$results,"des_stats.txt"),
      table.placement = "h",
      caption.placement="bottom", 
      include.rownames = FALSE, 
      include.colnames = TRUE, 
      hline.after = c(0, double_line, double_line, nrow(table1)))
```

There are two variable which formally do not have as many observations as the other: "Migrate" and "Length Stayed". We calculate the number of observations the actually have below:
```{r}
mmp_com_weather_stats %>%
  summarise("# Obs - Migrate" = sum(!is.na(M_U)),
            "# Obs - Length Stayed"  = sum(inus, na.rm = T))
```

We do a very similar process for our weather variables:
```{r}
com_weather = mmp_com_weather %>% filter(year != surveyyr) %>% 
  group_by(commun, year) %>% 
  summarise(across(c("prec_y_mean", "temp_avg_y_mean",
                     "temp_max_y_mean","temp_min_y_mean"), 
            ~  mean(.x, na.rm = TRUE))) %>% ungroup()

table2 = com_weather %>% 
  dplyr::summarise_at(.vars = "prec_y_mean", 
               .funs = c("Mean" = mean,"SD" = sd,"Min" = min,"Max" = max), 
               na.rm = T) 

table2 = cbind(Variable = "Precipitation (mm)", table2)


var_names  = c("Avg Temperature (ºC)", "Max Temperature (ºC)",
               "Min Temperature (ºC)")
i = 0
for (var in c("temp_avg_y_mean", 
              "temp_max_y_mean", "temp_min_y_mean")) {
  
 table_round = com_weather %>% 
  summarise_at(.vars = var, 
               .funs = c("Mean" = mean,"SD" = sd, "Min" = min,"Max" = max), 
               na.rm = T) 

i = i + 1
table_round = cbind(Variable = var_names[i], table_round) 
 
table2 = rbind(table2, table_round)
}

com_weather_sd =  com_weather %>%
  group_by(commun) %>%
  summarise(across(c("prec_y_mean", "temp_avg_y_mean",
                     "temp_max_y_mean","temp_min_y_mean"), 
            ~  sd(.x, na.rm = TRUE))) %>%
  ungroup() %>%
  summarise(across(c("prec_y_mean", "temp_avg_y_mean",
                     "temp_max_y_mean","temp_min_y_mean"), 
            ~  mean(.x, na.rm = TRUE), .names = "{.col}_sd"))

table2 = cbind(table2, "SD within" = t(com_weather_sd)) 

com_weather_sd_across =  com_weather %>% group_by(year) %>%
  summarise(across(c("prec_y_mean", "temp_avg_y_mean",
                     "temp_max_y_mean","temp_min_y_mean"), 
            ~  sd(.x, na.rm = TRUE))) %>%
  summarise(across(c("prec_y_mean", "temp_avg_y_mean",
                     "temp_max_y_mean","temp_min_y_mean"), 
            ~  mean(.x, na.rm = TRUE)))

table2 = cbind(table2, "SD across" = t(com_weather_sd_across))
rownames(table2) <- NULL

table2 = table2 %>%
  mutate(across("Mean":"SD across", ~ scales::comma(.x,
                                              accuracy = 0.01)))

n_com = com_weather %>%
  group_by(commun) %>% summarise(n_obs = n()) %>% nrow()

n_com = as.data.frame(cbind("Communities", t(rep(n_com, 6)))) %>%
  set_names(c("Variable", "Mean", "SD", 
              "Min", "Max", "SD within", "SD across")) %>%
  mutate(across("Mean":"SD across", ~ scales::comma(as.numeric(.x),
                                            accuracy = 1)))
  
n_obs = com_weather %>% 
  summarise("Mean" = n(),"SD" = n(),"Min" = n(),"Max" = n(), 
            "SD within" = n(), "SD across" = n()) %>%
  mutate(across("Mean":"SD across", ~ scales::comma(.x,
                                              accuracy = 1)))

n_obs = cbind(Variable = "Observations", n_obs)
table2 = rbind(table2, n_com, n_obs)

table2
```

```{r}
tab2 =xtable(table2, 
       caption = "Summary Statistics - Weather",
       digits  = 2, 
       align   = c("l","l","c","c","c","c","c","c"),
       label   = "desc_stats_weather")

print(tab2,file=paste0(dir$results,"des_stats_weather.txt"),
      table.placement = "h",
      caption.placement="bottom", 
      include.rownames = FALSE, 
      include.colnames = TRUE, 
      hline.after = c(0, 4, 4, nrow(table2)))
```


Lastly, we calculate the proportion of migrants in a given year. We will use this to interpret our results later on.
```{r}
prop_migrant = mmp_com_weather_stats %>%
  summarise("Prop of Migrants" = mean(M_U, na.rm = T),
            "Prop of Illegal Migrants" = mean(M_UIL, na.rm = TRUE),
            "Prop of Legal Migrants" = mean(M_UL, na.rm = TRUE))

prop_migrant
```
```{r}
write_csv(prop_migrant, 
          file=paste0(dir$constructed_data,"prop_mig.csv"))
```


```{r}
rm(list=ls(pattern="tab"))
rm(list=ls(patter=c("n_")))
rm(list=c("com_weather","com_weather_sd","com_weather_sd_across",
          "mmp_com_weather_stats", "mmp_com_weather_stay"))
```


# Plots 

We plot the variables of interest. First, historical deviations for weather variables to the migration decision:
```{r}
prec_m_dev = mean(mmp_com_weather$prec_y_mean_dev_lag, na.rm = T)

prcp_plt = ggplot(mmp_com_weather %>% 
         mutate(rank_prcp_dev = ntile(prec_y_mean_dev_lag, 10)) %>%
         group_by(rank_prcp_dev) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_prcp  = mean(prec_y_mean_dev_lag, 
                                         na.rm = TRUE))) + 
  geom_point(aes(x = norm_dev_prcp, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_prcp, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_prcp, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") +
  geom_vline(xintercept = 0) + 
  geom_vline(xintercept = prec_m_dev, 
             linetype = "dashed") + 
  labs(x = "Precipitation - Z-score (t-1)", 
       y = "Migrantion (% of Population)") +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17)) +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black"))))

prcp_plt + 
  ggtitle("Precipitacion and Migration") 
```


```{r}
ggsave(paste0(dir$fig,"prcp_dev_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
prcp_plt + 
  theme(text = element_text(size = 14)) 
```
```{r}
ggsave(paste0(dir$fig,"prcp_dev_plt_prest.png"), 
       width = 7, height = 4.5)
```


```{r}
tavg_m_dev = mean(mmp_com_weather$temp_avg_y_mean_dev_lag, na.rm = T)

tavg_plt = ggplot(mmp_com_weather %>% 
                    mutate(rank_tavg_dev = 
                             ntile(temp_avg_y_mean_dev_lag, 10)) %>%
         group_by(rank_tavg_dev) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tavg  = mean(temp_avg_y_mean_dev_lag, na.rm = TRUE), 
                   n_obs = n())) + 
  geom_point(aes(x = norm_dev_tavg, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tavg, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tavg, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Avg Temperature - Z-score (t-1)", 
       y = "Migration (% of Population)") + 
  geom_vline(xintercept = 0) + 
  geom_vline(xintercept = tavg_m_dev, 
             linetype = "dashed") + 
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black"))))
tavg_plt + 
  ggtitle("Average Temperature and Migration")
```


```{r}
ggsave(paste0(dir$fig,"tavg_dev_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tavg_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tavg_dev_plt_prest.png"), 
       width = 7, height = 4.5)
```



```{r}
tmax_m_dev = mean(mmp_com_weather$temp_max_y_mean_dev_lag, na.rm = T)

tmax_plt = ggplot(mmp_com_weather %>% mutate(rank_tmax_dev = ntile(temp_max_y_mean_dev_lag, 10)) %>%
         group_by(rank_tmax_dev) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tmax  = mean(temp_max_y_mean_dev_lag, na.rm = TRUE), 
                   n_obs = n())) + 
  geom_point(aes(x = norm_dev_tmax, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tmax, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmax, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  geom_vline(xintercept = 0) + 
    geom_vline(xintercept = tmax_m_dev, 
             linetype = "dashed") + 
  labs(x = "Max Temperature - Z-score (t-1)", y = "Migration (% of Population)") +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black"))))

tmax_plt + 
  ggtitle("Max Temperature and Migration") 
```


```{r}
ggsave(paste0(dir$fig,"tmax_dev_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_plt_prest.png"), 
       width = 7, height = 4.5)
```




```{r}
prcp_tmax_plt = ggarrange(prcp_plt + 
                            ggtitle("Precipitation and Migration") + 
                            labs(x = "Deviation (Z-score, t-1)"), 
                          tmax_plt + 
                            labs(y = "", x = "Deviation (Z -score, t-1)") +
                            ggtitle("Max Temperature and Migration"), 
          ncol = 2, common.legend = TRUE, legend = "bottom")

prcp_tmax_plt
```

```{r}
ggsave(paste0(dir$fig,"prcp_tmax_dev_plt.png"), 
       width = 9, height = 4.5, bg = "white")
```

#### Spanish
```{r}
prcp_plt = ggplot(mmp_com_weather %>% 
         mutate(rank_prcp_dev = ntile(prec_y_mean_dev_lag, 10)) %>%
         group_by(rank_prcp_dev) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_prcp  = mean(prec_y_mean_dev_lag, 
                                         na.rm = TRUE))) + 
  geom_point(aes(x = norm_dev_prcp, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_prcp, y = M_UIL_prop,shape = "Indocumentados"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_prcp, y = M_UL_prop, shape = "Documentados"), size = 3,
             color = "red") +
  geom_vline(xintercept = 0) + 
  geom_vline(xintercept = prec_m_dev, 
             linetype = "dashed") +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Indocumentados" = 16, 
                                           "Documentados" = 17)) +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black"))))
```

```{r}
tmax_plt = ggplot(mmp_com_weather %>% mutate(rank_tmax_dev = ntile(temp_max_y_mean_dev_lag, 10)) %>%
         group_by(rank_tmax_dev) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tmax  = mean(temp_max_y_mean_dev_lag, na.rm = TRUE), 
                   n_obs = n())) + 
  geom_point(aes(x = norm_dev_tmax, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tmax, y = M_UIL_prop,shape = "Indocumentados"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmax, y = M_UL_prop, shape = "Documentados"), size = 3,
             color = "red") + 
  geom_vline(xintercept = 0) + 
    geom_vline(xintercept = tmax_m_dev, 
             linetype = "dashed") +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Indocumentados" = 16, 
                                           "Documentados" = 17))  +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black"))))
```

```{r}
prcp_tmax_plt = ggarrange(prcp_plt + 
                            ggtitle("Precipitaciones y Migración") + 
                            labs(y = "Proporción de Migrantes (% de Población)",
                                 x = "Desvío en Z-score (t-1)"), 
                          tmax_plt + 
                            labs(y = "", 
                                 x = "Desvío en Z-score (t-1)") + 
                            ggtitle("Temperatura Máxima y Migración"), 
          ncol = 2, common.legend = TRUE, legend = "bottom")

prcp_tmax_plt
```

```{r}
ggsave(paste0(dir$fig,"prcp_tmax_dev_plt_CAF_post.png"), 
       width = 9, height = 4.5, bg = "white")
```

#### Back to English
```{r}
tmin_m_dev = mean(mmp_com_weather$temp_min_y_mean_dev_lag, na.rm = T)

tmin_plt = ggplot(mmp_com_weather %>% mutate(rank_tmin_dev = ntile(temp_min_y_mean_dev_lag, 10)) %>%
         group_by(rank_tmin_dev) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tmin  = mean(temp_min_y_mean_dev_lag, na.rm = TRUE), 
                   n_obs = n())) + 
  geom_point(aes(x = norm_dev_tmin, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tmin, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmin, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Min Temperature - Z-score (t-1)", y = "Migration (% of Population)") + 
  geom_vline(xintercept = 0) + 
      geom_vline(xintercept = tmin_m_dev, 
             linetype = "dashed") + 
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black"))))

tmin_plt + 
  ggtitle("Min Temperature and Migration")
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmin_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tavg_tmin_plt = ggarrange(tavg_plt + labs(x = "Deviation (Z-Score, t-1)") + ggtitle("Avg Temperature and Migration"), 
                          tmin_plt + labs(y = "", x = "Deviation - (Z-score, t-1)") + ggtitle("Min Temperature and Migration"), 
          ncol = 2, common.legend = TRUE, legend = "bottom")

tavg_tmin_plt
```

```{r}
ggsave(paste0(dir$fig,"tavg_tmin_dev_plt.png"), 
       width = 9, height = 4.5, bg = "white")
```

```{r}
rm(list=ls(patter="plt"))
```

# Regressions

```{r}
mmp_com_weather = mmp_com_weather %>% 
  filter((surveyyr - year) <= year_window)
```

## First Specification

We regress the migration decision against:

- Yearly (April-September) Z-score precipitations,
- Yearly (April-September) Z-score on average temperature,
- Yearly (April-September) Z-score on maximum temperature,
- Yearly (April-September) Z-score on minimum temperature.

```{r}
formula = "M_U ~ prec_y_mean_dev_lag | id + year"
reg_list_imm = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_U ~ ",i,"_y_mean_dev_lag | id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm = c(reg_list_imm, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_U = "Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(reg_list_imm[1:4],
         file = paste0(dir$results,"imm_results.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm[1:4])
```

```{r}
data.frame(marginal_prcp = reg_list_imm[[1]]$coefficients[[1]],
            marginal_tavg = reg_list_imm[[2]]$coefficients[[1]], 
            marginal_tmax = reg_list_imm[[3]]$coefficients[[1]], 
             marginal_tmin = reg_list_imm[[4]]$coefficients[[1]])/prop_migrant[[1,1]]
```


### Illegal Migration

We do the same analysis but only for the illegal migrants:
```{r}
formula = "M_UIL ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_il = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_UIL ~ ",i,"_y_mean_dev_lag | id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm_il = c(reg_list_imm_il, list(reg_round))
}
```

And summaries the results:
```{r}
setFixest_dict(c(M_UIL = "Illegal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(reg_list_imm_il[1:4], 
       file = paste0(dir$results,"imm_il_results.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)


etable(reg_list_imm_il[1:4])
```

```{r}
data.frame(marginal_prcp = reg_list_imm_il[[1]]$coefficients[[1]],
            marginal_tavg = reg_list_imm_il[[2]]$coefficients[[1]], 
            marginal_tmax = reg_list_imm_il[[3]]$coefficients[[1]], 
            marginal_tmin = reg_list_imm_il[[4]]$coefficients[[1]])/prop_migrant[[1,2]]
```


```{r}
beta_hat = data.frame(beta_prcp = reg_list_imm[[1]]$coefficients[[1]],
            beta_tavg = reg_list_imm[[2]]$coefficients[[1]], 
            beta_tmax = reg_list_imm[[3]]$coefficients[[1]], 
            beta_tmin = reg_list_imm[[4]]$coefficients[[1]])

write_csv(beta_hat, file=paste0(dir$constructed_data,"beta_hat.csv"))
```

```{r}
beta_var = data.frame(beta_prcp = reg_list_imm[[1]]$se[[1]],
            beta_tavg = reg_list_imm[[2]]$se[[1]], 
            beta_tmax = reg_list_imm[[3]]$se[[1]], 
            beta_tmin = reg_list_imm[[4]]$se[[1]])

write_csv(beta_var, file=paste0(dir$constructed_data,"beta_var.csv"))
```


### Legal Migrants

Lastly, we do the analysis for legal Migrants:
```{r}
formula = "M_UL ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_l = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_UL ~ ",i,"_y_mean_dev_lag | id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm_l = c(reg_list_imm_l, list(reg_round))
}
```

And summarise the result:
```{r}
setFixest_dict(c(M_UL = "Legal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(reg_list_imm_l[1:4],
       file = paste0(dir$results,"imm_l_results.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm_l[1:4])
```


```{r}
setFixest_dict(c(M_UL = "Legal Migrant", M_UIL = "Illegal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)")) 

etable(c(reg_list_imm_il[1:4],reg_list_imm_l[1:4]),
       file = paste0(dir$results,"imm_il_l_results.txt"),
       fitstat=c('n', 'ar2'), replace = TRUE)
```


## Second Specification

We do the same analysis allowing for non-linear effects:
```{r}
mmp_com_weather = 
  mmp_com_weather %>%
  mutate(across(ends_with("_y_mean_dev_lag"), 
                ~ .x^2, 
                .names = "{.col}_2"), 
         across(ends_with("_y_mean_dev_lag"), 
                ~ as.numeric(.x > 0)*.x, 
                .names = "{.col}_pos"))
```

```{r}
formula = 
  "M_U ~ prec_y_mean_dev_lag + prec_y_mean_dev_lag_2 | id + year"
reg_list_imm = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_U ~ ",i,"_y_mean_dev_lag "," + ",
                 i,"_y_mean_dev_lag_2 ",
                 "| id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm = c(reg_list_imm, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_U = "Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)", 
                 prec_y_mean_dev_lag_2     = "Dev Precipitation Sq (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag_2 = "Dev Avg Temp Sq (Z-score, t-1)",
                 temp_max_y_mean_dev_lag_2 = "Dev Max Temp Sq (Z-score, t-1)",
                 temp_min_y_mean_dev_lag_2 = "Dev Min Temp Sq (Z-score, t-1)"))

etable(reg_list_imm[1:4],
         file = paste0(dir$results,"imm_results_nl1.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm[1:4])
```

```{r}
formula = 
  "M_U ~ prec_y_mean_dev_lag + prec_y_mean_dev_lag_pos | id + year"
reg_list_imm = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_U ~ ",i,"_y_mean_dev_lag "," + ",
                 i,"_y_mean_dev_lag_pos ",
                 "| id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm = c(reg_list_imm, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_U = "Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)", 
                 prec_y_mean_dev_lag_pos     = "Dev Precipitation $>$ 0 (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag_pos = "Dev Avg Temp $>$ 0 (Z-score, t-1)",
                 temp_max_y_mean_dev_lag_pos = "Dev Max Temp $>$ 0 (Z-score, t-1)",
                 temp_min_y_mean_dev_lag_pos = "Dev Min Temp $>$ 0 (Z-score, t-1)"))

etable(reg_list_imm[1:4],
         file = paste0(dir$results,"imm_results_nl2.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm[1:4])
```

### Illegal Migration

We do the same analysis but only for the illegal migrants:
```{r}
formula = 
  "M_UIL ~ prec_y_mean_dev_lag + prec_y_mean_dev_lag_2 | id + year"
reg_list_imm_il1 = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_UIL ~ ",i,"_y_mean_dev_lag "," + ",
                 i,"_y_mean_dev_lag_2 ",
                 "| id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm_il1 = c(reg_list_imm_il1, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_UIL = "Illegal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)", 
                 prec_y_mean_dev_lag_2     = "Dev Precipitation Sq (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag_2 = "Dev Avg Temp Sq (Z-score, t-1)",
                 temp_max_y_mean_dev_lag_2 = "Dev Max Temp Sq (Z-score, t-1)",
                 temp_min_y_mean_dev_lag_2 = "Dev Min Temp Sq (Z-score, t-1)"))

etable(reg_list_imm_il1[1:4],
         file = paste0(dir$results,"imm_results_il_nl1.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm_il1[1:4])
```

```{r}
formula = 
  "M_UIL ~ prec_y_mean_dev_lag + prec_y_mean_dev_lag_pos | id + year"
reg_list_imm_il2 = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_UIL ~ ",i,"_y_mean_dev_lag "," + ",
                 i,"_y_mean_dev_lag_pos ",
                 "| id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm_il2 = c(reg_list_imm_il2, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_UIL = "Illegal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)", 
                 prec_y_mean_dev_lag_pos     = "Dev Precipitation $>$ 0 (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag_pos = "Dev Avg Temp $>$ 0 (Z-score, t-1)",
                 temp_max_y_mean_dev_lag_pos = "Dev Max Temp $>$ 0 (Z-score, t-1)",
                 temp_min_y_mean_dev_lag_pos = "Dev Min Temp $>$ 0 (Z-score, t-1)"))

etable(reg_list_imm_il2[1:4],
         file = paste0(dir$results,"imm_results_il_nl2.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm_il2[1:4])
```


### Legal Migrants

Lastly, we do the analysis for legal Migrants:
```{r}
formula = 
  "M_UL ~ prec_y_mean_dev_lag + prec_y_mean_dev_lag_2 | id + year"
reg_list_imm_l1 = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_UL ~ ",i,"_y_mean_dev_lag "," + ",
                 i,"_y_mean_dev_lag_2 ",
                 "| id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm_l1 = c(reg_list_imm_l1, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_UL = "Legal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)", 
                 prec_y_mean_dev_lag_2     = "Dev Precipitation Sq (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag_2 = "Dev Avg Temp Sq (Z-score, t-1)",
                 temp_max_y_mean_dev_lag_2 = "Dev Max Temp Sq (Z-score, t-1)",
                 temp_min_y_mean_dev_lag_2 = "Dev Min Temp Sq (Z-score, t-1)"))

etable(reg_list_imm_l1[1:4],
         file = paste0(dir$results,"imm_results_l_nl1.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm_l1[1:4])
```

```{r}
formula = 
  "M_UL ~ prec_y_mean_dev_lag + prec_y_mean_dev_lag_pos | id + year"
reg_list_imm_l2 = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
formula = paste0("M_UL ~ ",i,"_y_mean_dev_lag "," + ",
                 i,"_y_mean_dev_lag_pos ",
                 "| id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm_l2 = c(reg_list_imm_l2, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_UL = "Legal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)", 
                 prec_y_mean_dev_lag_pos     = "Dev Precipitation $>$ 0 (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag_pos = "Dev Avg Temp $>$ 0 (Z-score, t-1)",
                 temp_max_y_mean_dev_lag_pos = "Dev Max Temp $>$ 0 (Z-score, t-1)",
                 temp_min_y_mean_dev_lag_pos = "Dev Min Temp $>$ 0 (Z-score, t-1)"))

etable(reg_list_imm_l2[1:4],
         file = paste0(dir$results,"imm_results_l_nl2.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm_l2[1:4])
```


## Third Specification

We do the same analysis interacting temperature with precipitation:
```{r}
formula = "M_U ~ prec_y_mean_dev_lag*temp_avg_y_mean_dev_lag | id + year"
reg_list_imm = list(feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun"))

for (i in c("IL", "L")) {
formula = paste0("M_U", i, " ~ prec_y_mean_dev_lag*temp_avg_y_mean_dev_lag ",
                 "| id + year")
  
reg_round = feols(as.formula(formula), 
      data = mmp_com_weather, se = 'cluster', cluster = "commun")

reg_list_imm = c(reg_list_imm, list(reg_round))
}
```

And we summaries all the results in the following table:
```{r}
setFixest_dict(c(M_U = "Migrant",
                 M_UIL = "Illegal Migrant", 
                 M_UL = "Legal Migrant",
                 prec_y_mean_dev_lag     = "Dev Prec (t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (t-1)"))

etable(reg_list_imm[1:3],
         file = paste0(dir$results,"imm_inter_results.txt"), 
       fitstat=c('n', 'ar2'),
       replace = TRUE)

etable(reg_list_imm[1:3])
```