---
title:    'Agricultural Production'
author:   "Facundo Danza & Eungik Lee"
subtitle: "Plots and Regressions"
---

# Pre-analysis

First, we clean the R-environment:
```{r}
rm(list = ls())
gc()
```

Second, we load (and install) the needed packages:
```{r}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(data.table, tidyverse, janitor, readxl, fixest, ggpubr)
```

Third, we define the `theme_set`:
```{r}
theme_set(theme_bw())
```

Lastly, we set the working directories:
```{r}
dir              <- list()
dir$data         <- paste0(dirname(getwd()), "/data/")
dir$cons_data    <- paste0(dirname(getwd()), "/data/constructed/")
dir$ag           <- paste0(dirname(getwd()), "/data/ag_prod/spring_summer/")
dir$weather      <- paste0(dirname(getwd()), "/data/constructed/")
dir$results      <- paste0(dirname(getwd()), "/tables/agricultural/")
dir$fig          <- paste0(dirname(getwd()), "/figures/agricultural/")
```


# Daymet - Weather Data

## Load Data 

We start by opening the weather data on all municipalities of each *state* with at least one community in our sample (from the 2000 survey onward):
```{r}
mmp_state_tmax = read.csv(paste0(dir$weather, 
                             "weather_state_tmax_daymet.csv"))

mmp_state_weather = mmp_state_tmax

for (var in c("tmin", "prcp")) {
mmp_state_round = read.csv(paste0(dir$weather, 
                             "weather_state_",var,"_daymet.csv"))  

mmp_state_weather = left_join(mmp_state_weather, mmp_state_round, 
                            by = c("state", "municipio", "year","month","n_obs"))
}

rm(list = c("mmp_state_tmax", "mmp_state_round"))
```


Since our data is yearly rather than monthly, we take the average of each variable. Furthermore, we only keep the months from April to September, the wet season in Mexico:
```{r}
month_start = 4
month_end   = 9

mmp_state_weather_yr = mmp_state_weather %>% 
  rename(tmax = tmax_avg, tmin = tmin_avg) %>%
  filter(month >= month_start & month <= month_end) %>%
  group_by(state, municipio, year) %>%
  summarise(prcp_y_mean=mean(prcp_ttl),
            across(starts_with("t"), 
                   mean, .names = "{.col}_y_mean"))
```

```{r}
rm(mmp_state_weather)
```


## Normalize Data
As before, we need to "normalize" our dataset. We do so by taking the historical average over the period 1985-2014:
```{r}
start_yr_hist = 1985
end_yr_hist   = 2014

weather_norm = mmp_state_weather_yr %>%
  filter(year <= end_yr_hist & year >= start_yr_hist) %>%
  group_by(municipio, state) %>%
  summarise(across(ends_with("y_mean"),
                   mean, .names = "{.col}_hist"))
```

We then proceed by taking the deviations for the historical mean of:

- Precipitation in cl

- Temperature in ºC


```{r}
mmp_state_weather_yr = mmp_state_weather_yr %>% 
  left_join(weather_norm, by = c("municipio", "state"))

for (i in c("prcp_y","tmax_y","tmin_y")) {
  name1 = paste0(i,"_mean")
  name2 = paste0(i,"_mean_hist")
  name3 = paste0(i,"_mean_dev")
  mmp_state_weather_yr = cbind(mmp_state_weather_yr,
                          mmp_state_weather_yr[[name1]] - mmp_state_weather_yr[[name2]])
  names(mmp_state_weather_yr)[ncol(mmp_state_weather_yr)] <- name3
}

# Modify the precipitation
mmp_state_weather_yr = mmp_state_weather_yr %>%
  mutate(prcp_y_mean_dev = prcp_y_mean_dev/10)
```
```{r}
rm(weather_norm)
```


# Agricultural Data

## Totals

We load the total agricultural data. First, let's load the total plantation and harvested areas:
```{r}
total_prod_round = read_xls(paste0(dir$ag, "all/","ag_totals_2003.xls")) 
total_prod_round = total_prod_round[8:nrow(total_prod_round),2:ncol(total_prod_round)]
setnames(total_prod_round, 
         new = c("state", "district","municipio","planted_ha", "harvested_ha","value_1000pesos"))

total_prod_round$year = 2003
total_prod = total_prod_round

for (year in 2004:2019) {
  total_prod_round = read_xls(paste0(dir$ag, "all/","ag_totals_",year,".xls")) 
  total_prod_round = 
    total_prod_round[8:nrow(total_prod_round),2:ncol(total_prod_round)]
  setnames(total_prod_round, 
         new = c("state", "district","municipio","planted_ha",
                 "harvested_ha","value_1000pesos"))
  
  total_prod_round$year = year
  total_prod = rbind(total_prod, total_prod_round)
}

total_prod = total_prod %>% 
  mutate(across(ends_with("ha"), as.numeric))

rm(total_prod_round)
```


## Corn Production

### Grain

We load the data on corn production. Specifically, we load corn for grain:
```{r, output = FALSE}
corn_round = read_xls(paste0(dir$ag, "corn/grain/","corn_grain_2003.xls")) 
corn_round = corn_round[9:nrow(corn_round),2:ncol(corn_round)]
setnames(corn_round, 
          new = c("state", "district","municipio","planted_corn_ha",
                  "harvested_corn_ha","lost_corn_ha","prod_corn_ton",
                  "return_corn_ton_ha","return_corn_pesos_ton",
                  "value_corn_1000pesos"))
 
corn_round = corn_round %>%
  mutate(across("planted_corn_ha":"value_corn_1000pesos", as.numeric))

corn_round$year = 2003

corn_grain = corn_round

for (i in 2004:2019) {
  corn_round = read_xls(paste0(dir$ag, "corn/grain/",
                                    "corn_grain_",i,".xls")) 
  corn_round = 
    corn_round[9:nrow(corn_round),2:ncol(corn_round)]
  
  setnames(corn_round, 
          new = c("state", "district","municipio","planted_corn_ha",
                  "harvested_corn_ha","lost_corn_ha","prod_corn_ton",
                  "return_corn_ton_ha","return_corn_pesos_ton",
                  "value_corn_1000pesos"))
 
corn_round = corn_round %>%
  mutate(across("planted_corn_ha":"value_corn_1000pesos", as.numeric))

corn_round$year = i

corn_grain = rbind(corn_grain, corn_round)
}

corn_grain = corn_grain %>% group_by(state, municipio) %>%
  arrange(year, .by_group = T)
```


We re-name corn as corn for grain, just to be more explicit:
```{r}
for (i in 4:10) {
  name = names(corn_grain)[i]
  names(corn_grain)[i] = paste0(name, "_gr")
}

corn_grain = corn_grain %>%
  mutate(across(ends_with("gr"), as.numeric))
```


## Join

We then merge total production with corn-for-grain:
```{r}
total_prod = total_prod %>%
  full_join(corn_grain, by = c("state","district","municipio","year"))
```

We check the proportion of harvested land which correspond to corn:
```{r}
total_prod %>% 
  summarise(prop_corn_gr = mean(harvested_corn_ha_gr/harvested_ha, na.rm = T))
```

We fix the names of the municipalities and states to coincide with the daymet data:
```{r}
total_prod = total_prod %>%
  mutate(municipio = tolower(municipio))
  
total_prod = total_prod %>% 
  mutate(state = 
           case_when(state =="Michoacán" ~ "Michoacan",
                state =="Yucatán" ~ "Yucatan",
                state =="Nuevo León" ~ "Nuevo Leon",
                state =="Querétaro" ~ "Queretaro",
                state == "San Luis Potosí" ~ "San Luis Potosi",
                state == "México" ~ "Mexico",
                TRUE ~ state), 
         municipio = 
           case_when(municipio == "san juan mixtepec" 
                     & district == "Valles Centrales" ~
            "san juan mixtepec - valles centrales", 
            municipio == "san juan mixtepec" & district == "Huajuapan de León" ~
            "san juan mixtepec - huajuapan de leon", 
            municipio == "san pedro mixtepec" & district == "Valles Centrales" ~ 
              "san pedro mixtepec - valles centrales", 
            municipio == "san pedro mixtepec" & district == "Costa" ~ 
              "san pedro mixtepec - costa", 
               municipio == "jonacatepec" & state == "Morelos" ~ 
                       "jonacatepec de leandro valle",
            municipio == "san mateo yucutindoo" ~ "san mateo yucutindó",
            municipio == "h. v. tezoatlán de segura y luna, c. de la i.de o." ~ 
              "heroica villa tezoatlán de segura y luna",
                     TRUE ~ municipio))
```


```{r}
mmp_state_weather_yr = mmp_state_weather_yr %>% 
  mutate(municipio = tolower(municipio)) %>%
  mutate(municipio = case_when(municipio == "san juan mixtepec -dto. 26 -" ~ 
                     "san juan mixtepec - valles centrales",
            municipio == "san juan mixtepec -dto. 08 -" ~ 
              "san juan mixtepec - huajuapan de leon", 
            municipio == "san pedro mixtepec -dto. 22 -" ~ 
              "san pedro mixtepec - costa", 
            municipio == "san pedro mixtepec -dto. 26 -" ~ 
              "san pedro mixtepec - valles centrales", 
            TRUE ~ municipio))
```

```{r}
mmp_state_ag = mmp_state_weather_yr  %>%
  left_join(total_prod, by = c("state","municipio","year")) %>%
  filter(year > 2002)
```


# Plots

```{r}
harv_avg = mmp_state_ag %>% filter(harvested_ha > 0) %>%
  group_by(state, municipio) %>%
  summarise(harv_ha_mean=mean(harvested_ha, na.rm= T))
```

## Harvested Area

We plot the variables of interest:
```{r}
prec_m_dev = mean(mmp_state_ag$prcp_y_mean_dev, na.rm = T)

prcp_harv_plt = ggplot(mmp_state_ag %>% filter(harvested_ha != 0) %>% 
         left_join(harv_avg, by = c("state", "municipio")) %>%
         mutate(harv_dev = (harvested_ha - harv_ha_mean)/harv_ha_mean) %>%
         mutate(rank_prcp_dev = ntile(prcp_y_mean_dev, 10)) %>%
         group_by(rank_prcp_dev) %>% 
         summarise(harv_dev       = mean(harv_dev, na.rm = TRUE)*100,
                   norm_dev_prcp  = mean(prcp_y_mean_dev, na.rm = TRUE)), 
       aes(x = norm_dev_prcp, y = harv_dev)) + 
  geom_point(shape = 15, size = 3, 
             color = "black")  + 
  geom_smooth(color = "darkgreen") +
  labs(x = "Precipitation (cl) - Deviation Historical Mean", y = "Harvested Area - Deviation Historical Mean (%)") + 
  geom_vline(xintercept = 0) + 
  geom_vline(xintercept = prec_m_dev, 
             linetype = "dashed") 

prcp_harv_plt + ggtitle("Agricultural Production", 
         subtitle = "Harvested Area")
```



```{r}
ggsave(paste0(dir$fig,"prcp_dev_harv_state_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
prcp_harv_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"prcp_dev_harv_state_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_m_dev = mean(mmp_state_ag$tmax_y_mean_dev, na.rm = T)

tmax_harv_plt = ggplot(mmp_state_ag %>% filter(harvested_ha != 0) %>% 
         left_join(harv_avg, by = c("state", "municipio")) %>%
         mutate(harv_dev = (harvested_ha - harv_ha_mean)/harv_ha_mean) %>%
         mutate(rank_tmax_dev = ntile(tmax_y_mean_dev, 10)) %>%
         group_by(rank_tmax_dev) %>% 
         summarise(harv_dev       = mean(harv_dev, na.rm = TRUE)*100,
                   norm_dev_tmax  = mean(tmax_y_mean_dev, na.rm = TRUE)), 
       aes(x = norm_dev_tmax, y = harv_dev)) + 
  geom_point(shape = 15, size = 3, 
             color = "black")  + 
  geom_smooth(color = "darkgreen") + 
  labs(x = "Max Temperature (ºC) - Deviation Historical Mean", y = "Harvested Area - Deviation Historical Mean (%)") +
  geom_vline(xintercept = 0) + 
  geom_vline(xintercept = tmax_m_dev, 
             linetype = "dashed") 

tmax_harv_plt + 
  ggtitle("Agricultural Production", 
          subtitle = "Harvested Area")
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_harv_state_plt.png"), 
       width = 7, height = 4.5)
```
```{r}
tmax_harv_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_harv_state_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
prcp_tmax_plt = ggarrange(prcp_harv_plt + ggtitle("Precipitation and Harvested Land") + labs(x = "Deviation Historical Mean (cl)"), 
                          tmax_harv_plt + labs(y = "", x = "Deviation Historical Mean (ºC)") + ggtitle("Max Temperature and Harvested Land"), 
          ncol = 2, common.legend = TRUE, legend = "bottom")

prcp_tmax_plt
```


```{r}
ggsave(paste0(dir$fig,"prcp_tmax_dev_harv_state_plt.png"), 
       width = 9, height = 4.5)
```

```{r}
tmin_m_dev = mean(mmp_state_ag$tmin_y_mean_dev, na.rm = T)

tmin_harv_plt = ggplot(mmp_state_ag %>% filter(harvested_ha != 0) %>% 
         left_join(harv_avg, by = c("state", "municipio")) %>%
         mutate(harv_dev = (harvested_ha - harv_ha_mean)/harv_ha_mean) %>%
         mutate(rank_tmin_dev = ntile(tmin_y_mean_dev, 10)) %>%
         group_by(rank_tmin_dev) %>% 
         summarise(harv_dev        = mean(harv_dev, na.rm = TRUE)*100,
                   norm_dev_tmin  = mean(tmin_y_mean_dev, na.rm = TRUE)),
       aes(x = norm_dev_tmin, y = harv_dev)) + 
  geom_point(shape = 15, size = 3, 
             color = "black")  + 
  geom_smooth(color = "darkgreen") + 
  labs(x = "Min Temperature - Deviation Historical Mean (ºC)", y = "Harvested Area - Deviation Historical Mean (%)") +
  geom_vline(xintercept = 0) + 
  geom_vline(xintercept = tmin_m_dev, 
             linetype = "dashed") 

tmin_harv_plt +
  ggtitle("Min Temperature and Harvested Land")
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_harv_state_plt.png"), 
       width = 7, height = 4.5)
```


```{r}
tmin_harv_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_harv_state_plt_prest.png"), 
       width = 7, height = 4.5)
```

# Regressions

## Totals

We then run the regressions:
```{r}
mmp_state_ag = mmp_state_ag %>%
  mutate(id = as.factor(paste0(state,"-",municipio)))

formula = "log(harvested_ha) ~ prcp_y_mean_dev | id + year"
regression = feols(as.formula(formula), 
      data = mmp_state_ag, se = 'cluster', cluster = "id")
regression_list_tot = list(regression)

for (i in c("tmax", "tmin")) {
formula = paste0("log(harvested_ha) ~ ",i,"_y_mean_dev | id + year")
regression = feols(as.formula(formula), 
      data = mmp_state_ag, se = 'cluster', cluster = "id")
regression_list_tot = c(regression_list_tot,list(regression))
}
```

```{r}
setFixest_dict(c(`log(harvested_ha)` = "Log (Harv Area) - Ha",
                 prcp_y_mean_dev   = "Dev Precipiation (cl)", 
                 tmax_y_mean_dev   = "Dev Max Temp (ºC)",
                 tmin_y_mean_dev   = "Dev Min Temp (ºC)"))

etable(regression_list_tot[1:4], 
       file = paste0(dir$results,"harv_state_results.txt"),
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(regression_list_tot[1:4])
```


## Corn Production - Grain
```{r}
formula = "log(prod_corn_ton_gr) ~ prcp_y_mean_dev | id + year"
regression = feols(as.formula(formula), 
      data = mmp_state_ag, se = 'cluster', cluster = "id")
regression_list_corn = list(regression)

for (i in c("tmax", "tmin")) {
formula = paste0("log(prod_corn_ton_gr) ~ ",i,"_y_mean_dev | id + year")

regression = feols(as.formula(formula), 
      data = mmp_state_ag, se = 'cluster', cluster = "id")
regression_list_corn = c(regression_list_corn,list(regression))
}
```

```{r}
setFixest_dict(c(`log(prod_corn_ton_gr)` = "Log (Corn Prod) - Gr, Ton",
                 `log(harvested_ha)`  = "Log (Harv Area) - Ha",
                 prcp_y_mean_dev   = "Dev Precipiation (cl)", 
                 tmax_y_mean_dev   = "Dev Max Temp (ºC)",
                 tmin_y_mean_dev   = "Dev Min Temp (ºC)"))

etable(regression_list_corn[1:4], 
       file = paste0(dir$results,"corn_state_results.txt"),
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(regression_list_corn[1:4])
```

```{r}
etable(c(regression_list_tot[1:4],regression_list_corn[1:4]), 
       file = paste0(dir$results,"ag_state_results.txt"),
       fitstat=c('n', 'ar2'), replace = TRUE)
```