---
title:  'Migration - Projections'
author: "Facundo Danza & Eungik Lee"
---

# Pre-analysis

First, we clean the R-environment:
```{r}
rm(list = ls())
gc()
```

Then, we load (and install) the needed packages:
```{r}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(data.table, tidyverse, janitor, readxl, xtable, scales, 
               future, future.apply, tictoc)
```

We then set the directories in which we have the data:
```{r}
dir = list()
dir$data         <- paste0(dirname(getwd()), "/data/")
dir$beta         <- paste0(dirname(getwd()), "/data/constructed/")
dir$commun       <- paste0(dirname(getwd()), "/data/commun/")
dir$weather      <- 
  paste0(dirname(getwd()), "/data/confidential/constructed/")
dir$constructed_data  <- 
  paste0(dirname(getwd()), "/data/confidential/constructed/")
dir$meteoblue    <- 
  paste0(dirname(getwd()), "/data/confidential/meteoblue/")
dir$mmp_final    <- 
  paste0(dirname(getwd()), "/data/confidential/constructed/")
dir$results      <- paste0(dirname(getwd()), "/tables/projection/")
```


# Terraclimate - Weather Data

## Historical Data 

We start by opening the weather data on the municipalities for which some communities were surveyed in MMP (from the 2000 survey onward):
```{r}
mmp_mun_tmax = read.csv(paste0(dir$weather, 
                             "weather_mun_tmax_daymet.csv"))

mmp_mun_weather = mmp_mun_tmax

for (var in c("tmin", "prcp")) {
mmp_mun_round = read.csv(paste0(dir$weather, 
                             "weather_mun_",var,"_daymet.csv"))  

mmp_mun_weather = left_join(mmp_mun_weather, mmp_mun_round, 
                            by = c("state", "municipio", "year","month","n_obs"))
}

rm(list = c("mmp_mun_tmax", "mmp_mun_round"))
```


Since our data is yearly rather than monthly, we take the average of each variable, Furthermore, we only keep the months from April to September, the wet season in Mexico:
```{r}
month_start = 4
month_end   = 9

mmp_mun_weather_yr = mmp_mun_weather %>% 
  rename(tmax = tmax_avg, tmin = tmin_avg) %>%
  filter(month >= month_start & month <= month_end) %>%
  group_by(state, municipio, year) %>%
  summarise(prcp_y_mean=mean(prcp_ttl),
            across(starts_with("t"), 
                   mean, .names = "{.col}_y_mean"))

```

As before, we need to normalize our dataset. We do so by taking the historical average over the period 1985-2014:
```{r}
start_yr_hist = 1985
end_yr_hist   = 2014

weather_norm = mmp_mun_weather_yr %>%
  filter(year <= end_yr_hist & year >= start_yr_hist) %>%
  group_by(municipio, state) %>%
  summarise(across(ends_with("y_mean"),
                   mean, .names = "{.col}_hist"))

```

## Projections

### 2C
We load the weather projections:
```{r}
mmp_mun_tmax_2C = read.csv(paste0(dir$weather, 
                               "weather_mun_tmax_proj2C.csv"))

mmp_mun_weather_2C = mmp_mun_tmax_2C

for (var in c("tmin", "prcp")) {
  mmp_mun_round = read.csv(paste0(dir$weather, 
                                  "weather_mun_",var,"_proj2C.csv"))  
  
  mmp_mun_weather_2C = left_join(mmp_mun_weather_2C, mmp_mun_round, 
                              by = c("state", "municipio", "year","month","n_obs"))
}

rm(list = c("mmp_mun_tmax_2C", "mmp_mun_round"))
```

Since our data is yearly rather than monthly, we take the average of each variable, Furthermore, we only keep the months from April to September, the wet season for Mexican crops:
```{r}
month_start = 4
month_end   = 9

mmp_mun_weather_2C = mmp_mun_weather_2C %>% 
  rename(tmax = tmax_avg, tmin = tmin_avg) %>%
  filter(month >= month_start & month <= month_end) %>%
  group_by(state, municipio) %>%
  summarise(prcp_y_mean=mean(ppt_avg),
            across(starts_with("t"), 
                   mean, .names = "{.col}_y_mean"))
```


We then proceed by taking the deviations for the historical mean of:

- Precipitation in cl

- Temperature in ºC

```{r}
mmp_mun_weather_2C = mmp_mun_weather_2C %>% 
  right_join(weather_norm, by = c("municipio", "state"))

for (i in c("prcp_y","tmax_y","tmin_y")) {
  name1 = paste0(i,"_mean")
  name2 = paste0(i,"_mean_hist")
  name3 = paste0(i,"_mean_dev")
  mmp_mun_weather_2C = cbind(mmp_mun_weather_2C,
                          mmp_mun_weather_2C[[name1]] - mmp_mun_weather_2C[[name2]])
  names(mmp_mun_weather_2C)[ncol(mmp_mun_weather_2C)] <- name3
}

# Modify the precipitation
mmp_mun_weather_2C = mmp_mun_weather_2C %>%
  mutate(prcp_y_mean_dev = prcp_y_mean_dev/10)
```

We load our estimates of the causal effect of weather on migration. Specifically, we load the beta_hat estimated in our main analysis:
```{r}
beta_hat = read.csv(paste0(dir$beta,"beta_hat.csv"))
```

And its variance:
```{r}
beta_var = read.csv(paste0(dir$beta,"beta_var.csv"))
```


And we simply project the immigration by multiply the effect of weather on migration over the expected change on weather:
```{r}
mmp_mun_weather_2C = mmp_mun_weather_2C %>% ungroup() %>%
  mutate(imm_proj_prcp = prcp_y_mean_dev*beta_hat$beta_prcp,
         imm_proj_tmax = tmax_y_mean_dev*beta_hat$beta_tmax,
         imm_proj_tmin = tmin_y_mean_dev*beta_hat$beta_tmin)
```


Since beta is an estimate, we consider the variance of it when doing projections. Specifically, we bootstrap of potential beta's:
```{r}
loop_beta_2C = 
  function(i, 
           beta_m   = beta_hat,
           beta_v   = beta_var) {
  beta_round = data.frame(beta_prcp = 
                            rnorm(1, mean = beta_m$beta_prcp, 
                                sd = beta_v$beta_prcp))
  j = 1
  for (var in c("tmax", "tmin")) {
    j = j + 1
    name = paste0("beta_",var)
    beta = data.frame(beta = rnorm(1, mean = beta_m[[j]], 
                                  sd = beta_v[[j]]))
    names(beta) <- name
    beta_round = cbind(beta_round, beta)
  }
  
    
  mmp_mun_weather_2C_round = mmp_mun_weather_2C %>%
  mutate(imm_proj_prcp = prcp_y_mean_dev*beta_round$beta_prcp,
         imm_proj_tmax = tmax_y_mean_dev*beta_round$beta_tmax,
         imm_proj_tmin = tmin_y_mean_dev*beta_round$beta_tmin) %>%
    summarise(imm_proj_prcp = mean(imm_proj_prcp), 
              imm_proj_tmax = mean(imm_proj_tmax),
              imm_proj_tmin = mean(imm_proj_tmin))
  

  return(mmp_mun_weather_2C_round) 
}
```

```{r}
tic()
mmp_mun_weather_2C_boot = 
  future_lapply(1:10000, 
  loop_beta_2C, future.seed = 8312022) %>%
  bind_rows()
toc()
```

And take the average of such result:
```{r}
table_2C_i = mmp_mun_weather_2C %>%
  summarise("dev_proj_Precipitation (cl)"     = mean(prcp_y_mean_dev),
            "dev_proj_Max Temp (ºC)" = mean(tmax_y_mean_dev), 
            "dev_proj_Min Temp (ºC)" = mean(tmin_y_mean_dev)) %>%
  pivot_longer(cols = starts_with("dev_proj_"),
               names_to     = "Variable",
               values_to    = "Deviation",
               names_prefix = "dev_proj_")

table_2C_ii = mmp_mun_weather_2C %>%
  summarise("imm_proj_Precipitation (cl)"         = mean(imm_proj_prcp)*100,
            "imm_proj_Max Temp (ºC)"     = mean(imm_proj_tmax)*100, 
            "imm_proj_Min Temp (ºC)"     = mean(imm_proj_tmin)*100) %>%
  pivot_longer(cols = starts_with("imm_proj_"),
               names_to     = "Variable", 
               values_to    = "Migration (p.p)", 
               names_prefix = "imm_proj_")


table_2C = table_2C_i %>% 
  left_join(table_2C_ii, by = "Variable")
table_2C
```

```{r}
boot_sd = mmp_mun_weather_2C_boot %>%
  summarise("imm_proj_Precipitation (cl)" = sd(imm_proj_prcp)*100, 
            "imm_proj_Max Temp (ºC)" = sd(imm_proj_tmax)*100,
            "imm_proj_Min Temp (ºC)" = sd(imm_proj_tmin)*100)
```

```{r}
table_2C_i_SD = mmp_mun_weather_2C %>%
  summarise("dev_proj_Precipitation (cl)"     = sd(prcp_y_mean_dev),
            "dev_proj_Max Temp (ºC)" = sd(tmax_y_mean_dev), 
            "dev_proj_Min Temp (ºC)" = sd(tmin_y_mean_dev)) %>%
  pivot_longer(cols = starts_with("dev_proj_"),
               names_to     = "Variable",
               values_to    = "Deviation",
               names_prefix = "dev_proj_")

table_2C_ii_SD = boot_sd %>%
  pivot_longer(cols = starts_with("imm_proj_"),
               names_to     = "Variable", 
               values_to    = "Migration (p.p)", 
               names_prefix = "imm_proj_")

table_2C_SD = table_2C_i_SD %>% 
                       left_join(table_2C_ii_SD, by = "Variable") %>%
  mutate(across("Deviation":"Migration (p.p)", ~ paste0("(",round(.x,3),")")))

table_2C_SD
```

### 4C

We do exactly the same, but for an projected increase in global temperature of 4ºC:
```{r}
mmp_mun_tmax_4C = read.csv(paste0(dir$weather, 
                                  "weather_mun_tmax_proj4C.csv"))

mmp_mun_weather_4C = mmp_mun_tmax_4C

for (var in c("tmin", "prcp")) {
  mmp_mun_round = read.csv(paste0(dir$weather, 
                                  "weather_mun_",var,"_proj4C.csv"))  
  
  mmp_mun_weather_4C = left_join(mmp_mun_weather_4C, mmp_mun_round, 
                                 by = c("state", "municipio", "year","month","n_obs"))
}

rm(list = c("mmp_mun_tmax_4C", "mmp_mun_round"))
```

Since our data is yearly rather than monthly, we take the average of each variable, Furthermore, we only keep the months from April to September, the wet season for Mexican crops:
```{r}
month_start = 4
month_end   = 9

mmp_mun_weather_4C = mmp_mun_weather_4C %>% 
  rename(prcp_avg = ppt_avg, tmax = tmax_avg, tmin = tmin_avg) %>%
  filter(month >= month_start & month <= month_end) %>%
  group_by(state, municipio) %>%
  summarise(prcp_y_mean=mean(prcp_avg),
            across(starts_with("t"), 
                   mean, .names = "{.col}_y_mean"))
```


We then proceed by taking the deviations for the historical mean:
  
- Precipitation in cl

- Temprature in ºC

```{r}
mmp_mun_weather_4C = mmp_mun_weather_4C %>% 
  right_join(weather_norm, by = c("municipio", "state"))

for (i in c("prcp_y","tmax_y","tmin_y")) {
  name1 = paste0(i,"_mean")
  name2 = paste0(i,"_mean_hist")
  name3 = paste0(i,"_mean_dev")
  mmp_mun_weather_4C = cbind(mmp_mun_weather_4C,
                             mmp_mun_weather_4C[[name1]] - mmp_mun_weather_4C[[name2]])
  names(mmp_mun_weather_4C)[ncol(mmp_mun_weather_4C)] <- name3
}

# Modify the precipitation
mmp_mun_weather_4C = mmp_mun_weather_4C %>%
  mutate(prcp_y_mean_dev = prcp_y_mean_dev/10)
```


We simply project the immigration by multiply the effect of weather on immigration over the expected change on weather:
```{r}
mmp_mun_weather_4C = mmp_mun_weather_4C %>% ungroup() %>%
  mutate(imm_proj_prcp = prcp_y_mean_dev*beta_hat$beta_prcp,
         imm_proj_tmax = tmax_y_mean_dev*beta_hat$beta_tmax,
         imm_proj_tmin = tmin_y_mean_dev*beta_hat$beta_tmin)
```


Since beta is an estimate, we consider the variance of it when doing projections. Specifically, we bootstrap of potential beta's:
```{r}
loop_beta_4C = 
  function(i, 
           beta_m   = beta_hat,
           beta_v   = beta_var) {
  beta_round = data.frame(beta_prcp = 
                            rnorm(1, mean = beta_m$beta_prcp, 
                                sd = beta_v$beta_prcp))
  j = 1
  for (var in c("tmax", "tmin")) {
    j = j + 1
    name = paste0("beta_",var)
    beta = data.frame(beta = rnorm(1, mean = beta_m[[j]], 
                                  sd = beta_v[[j]]))
    names(beta) <- name
    beta_round = cbind(beta_round, beta)
  }
  
    
  mmp_mun_weather_4C_round = mmp_mun_weather_4C %>%
  mutate(imm_proj_prcp = prcp_y_mean_dev*beta_round$beta_prcp,
         imm_proj_tmax = tmax_y_mean_dev*beta_round$beta_tmax,
         imm_proj_tmin = tmin_y_mean_dev*beta_round$beta_tmin) %>%
    summarise(imm_proj_prcp = mean(imm_proj_prcp), 
              imm_proj_tmax = mean(imm_proj_tmax),
              imm_proj_tmin = mean(imm_proj_tmin))
  

  return(mmp_mun_weather_4C_round) 
}
```

```{r}
tic()
mmp_mun_weather_4C_boot = 
  future_lapply(1:10000, 
  loop_beta_4C, future.seed = 8312022) %>%
  bind_rows()
toc()
```


We take the average of such result:
```{r}
table_4C_i = mmp_mun_weather_4C %>%
  summarise("dev_proj_Precipitation (cl)"     = mean(prcp_y_mean_dev),
            "dev_proj_Max Temp (ºC)" = mean(tmax_y_mean_dev), 
            "dev_proj_Min Temp (ºC)" = mean(tmin_y_mean_dev)) %>%
  pivot_longer(cols = starts_with("dev_proj_"),
               names_to     = "Variable",
               values_to    = "Deviation",
               names_prefix = "dev_proj_")

table_4C_ii = mmp_mun_weather_4C %>%
  summarise("imm_proj_Precipitation (cl)"         = mean(imm_proj_prcp)*100,
            "imm_proj_Max Temp (ºC)"     = mean(imm_proj_tmax)*100, 
            "imm_proj_Min Temp (ºC)"     = mean(imm_proj_tmin)*100) %>%
  pivot_longer(cols = starts_with("imm_proj_"),
               names_to     = "Variable", 
               values_to    = "Migration (p.p)", 
               names_prefix = "imm_proj_")


table_4C = table_4C_i %>% 
                       left_join(table_4C_ii, by = "Variable")
table_4C
```

```{r}
boot_sd = mmp_mun_weather_4C_boot %>%
  summarise("imm_proj_Precipitation (cl)" = sd(imm_proj_prcp)*100, 
            "imm_proj_Max Temp (ºC)" = sd(imm_proj_tmax)*100,
            "imm_proj_Min Temp (ºC)" = sd(imm_proj_tmin)*100)
```

```{r}
table_4C_i_SD = mmp_mun_weather_4C %>%
  summarise("dev_proj_Precipitation (cl)"     = sd(prcp_y_mean_dev),
            "dev_proj_Max Temp (ºC)" = sd(tmax_y_mean_dev), 
            "dev_proj_Min Temp (ºC)" = sd(tmin_y_mean_dev)) %>%
  pivot_longer(cols = starts_with("dev_proj_"),
               names_to     = "Variable",
               values_to    = "Deviation",
               names_prefix = "dev_proj_")

table_4C_ii_SD = boot_sd %>%
  pivot_longer(cols = starts_with("imm_proj_"),
               names_to     = "Variable", 
               values_to    = "Migration (p.p)", 
               names_prefix = "imm_proj_") 

table_4C_SD = table_4C_i_SD %>% 
                       left_join(table_4C_ii_SD, by = "Variable") %>%
  mutate(across("Deviation":"Migration (p.p)", ~ paste0("(",round(.x,3),")")))

table_4C_SD
```


### Both

We add both results in one table:
```{r}
table_2C_string = table_2C %>% 
  mutate(across("Deviation":"Migration (p.p)", 
                ~ scales::comma(.x,accuracy = .01))) 

table_2C_all = 
  rbind(table_2C_string[1,], table_2C_SD[1,],
        table_2C_string[2,], table_2C_SD[2,],
        table_2C_string[3,], table_2C_SD[3,])

table_2C_all[c(2,4,6), 1] <- ""
table_2C_all
```

```{r}
table_4C_string = table_4C %>% 
  mutate(across("Deviation":"Migration (p.p)", 
                ~ scales::comma(.x,accuracy = .01))) 

table_4C_all = 
  rbind(table_4C_string[1,], table_4C_SD[1,],
        table_4C_string[2,], table_4C_SD[2,],
        table_4C_string[3,], table_4C_SD[3,])

table_4C_all[c(2,4,6), 1] <- ""
table_4C_all
```

```{r}
tab_both =xtable(cbind(table_2C_all,table_4C_all[,2:3]), 
              caption = "Projected Illegal Migration",
              align   = c("c","l|","c","c|","c","c"),
              label   = "proj_imm")

print(tab_both,file=paste0(dir$results,"proj_imm.txt"),
      table.placement = "h",
      caption.placement="bottom", 
      include.rownames = FALSE, 
      include.colnames = TRUE, 
      hline.after = c(0, nrow(tab_both)), 
      add.to.row = list(pos = list(-1), command =c(" & \\multicolumn{2}{|c}{2ºC} & \\multicolumn{2}{|c}{4ºC} \\\\")))
```