---
title:  'MMP and the Weather: Heterogeneity'
author: "Facundo Danza & Eungik Lee"
---

# Pre-analysis

First, we clean the R environment:
```{r}
rm(list = ls())
gc()
```

Then, we load the packages 
```{r}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(tidyverse, data.table, janitor, dplyr, fixest, expss, ggpubr)
```

Define the `theme_set`
```{r}
theme_set(theme_bw())
```


Lastly, we set the directories in which we have the data:
```{r}
dir = list()
dir$root    <- dirname(getwd())
dir$data    <- paste0(dirname(getwd()), "/data/")
dir$weather    <- 
  paste0(dirname(getwd()), "/data/confidential/meteoblue/")
dir$results    <- paste0(dirname(getwd()), "/tables/heterogeneity/")
dir$constructed_data    <- 
  paste0(dirname(getwd()), "/data/confidential/constructed/")
dir$fig    <- paste0(dirname(getwd()), "/figures/heterogeneity/")
```


# Meteoblue - Weather Data

## Load the data

First, we load the daily weather data (and drop the missing values of it):
```{r}
weather_daily = read.csv(paste0(dir$weather, "weather.csv")) %>%
              filter(!is.na(day))
```

Since our data is annual rather than daily, we take the average (or sum) of each variable, Furthermore, we only keep the months from April to September, the wet season for Mexican crops:
```{r}
month_start = 4
month_end   = 9

weather_year = weather_daily %>% 
  filter(month >= month_start & 
           month <= month_end) %>%
  group_by(commun, year, month) %>%
  summarise(prec_m_sum=sum(precipitation),
            across(starts_with("temp"), mean)) %>%
  group_by(commun, year) %>%
  summarise(prec_y_mean=mean(prec_m_sum),
            across(starts_with("temp"), 
                   mean, .names = "{.col}_y_mean"))
```


# Mexican Migration Project (MMP)

## Load the data
We first load the data on MMP. We have already clean the data - you can find the code as "mmp_data_analysis.Rmd."
```{r}
mmp = 
  read.csv(paste0(dir$constructed_data,"mmp_individual_clean.csv")) %>%
  filter(year >= 1989 & pop_2010 <= 100000) # keep only up to mid-town cities)
```


# Merge MMP and Weather

We, then, merge data on weather and MMP:
```{r}
mmp_com_weather = left_join(mmp, 
                            weather_year, by = c("commun","year")) %>%
  filter(!is.na(prec_y_mean))
```

Finally label some variables of interest:
```{r}
mmp_com_weather = mmp_com_weather %>%
  apply_labels(M_U   = "Migrant",
               M_UIL = "Illegal Migrant",
               M_UL  = "Legal Migrant",
               prec_y_mean = "Prec (Avg)",
               temp_avg_y_mean = "Temp (Avg)",
               temp_max_y_mean = "Max Temp (Avg)",
               temp_min_y_mean = "Min Temp (Avg)")
```


## Normalize Weather

First we need to "standarized" our weather data. That is, we find the historical average and standard devitation over the period 1985-2019:
```{r}
start_yr_hist = 1985
end_yr_hist   = 2019

weather_norm = weather_year %>%
  filter(year <= end_yr_hist & year >= start_yr_hist) %>%
  group_by(commun) %>%
  summarise(across(ends_with("y_mean"),
                   mean, .names = "{.col}_hist"), 
            across(ends_with("y_mean"),
                   sd, .names = "{.col}_sd_hist"))
```


We add this "normalized" dataset to the pre-existing one. Furthermore, we only keep 10-year windows backwards:
```{r}
year_window = 11
mmp_com_weather = left_join(mmp_com_weather, 
                            weather_norm, by = "commun")

mmp_com_weather = mmp_com_weather %>% 
  filter((surveyyr - year) <= year_window)
```


We then proceed by taking the z-score for each weather variable. Specifically, we define deviations:
```{r}
mmp_com_weather = 
  mmp_com_weather %>% 
  mutate(prec_y_mean_dev = 
           (prec_y_mean - prec_y_mean_hist)/prec_y_mean_sd_hist, 
         temp_avg_y_mean_dev = 
           (temp_avg_y_mean - temp_avg_y_mean_hist)/temp_avg_y_mean_sd_hist, 
         temp_max_y_mean_dev = 
           (temp_max_y_mean - temp_max_y_mean_hist)/temp_max_y_mean_sd_hist, 
         temp_min_y_mean_dev = 
           (temp_min_y_mean - temp_min_y_mean_hist)/temp_min_y_mean_sd_hist)
```

We also take the lag variables, which we believe is the relevant timing for the migration decision,
```{r}
mmp_com_weather = mmp_com_weather %>%
  arrange(id, year)

mmp_com_weather = mmp_com_weather %>%
  group_by(id) %>%
  mutate(prec_y_mean_dev_lag = lag(prec_y_mean_dev),
         across(starts_with("temp") & ends_with("y_mean_dev"), ~ lag(.x),
                .names = "{.col}_lag"))
```


# Plots 

We plot the variables of interest. 

## Agricultural Worker

```{r}
mmp_com_weather = mmp_com_weather %>%
  arrange(id, year) %>%
  mutate(ag_work_lag = lag(ag_work))
```


```{r}
prec_m_dev = mean(mmp_com_weather$prec_y_mean_dev_lag, na.rm = T)

prcp_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(ag_work_lag)) %>%
                       mutate(rank_prcp_dev = ntile(prec_y_mean_dev_lag, 10)) %>%
                       group_by(rank_prcp_dev, ag_work_lag) %>% 
                       summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                                 M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                                 M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                                 norm_dev_prcp  = mean(prec_y_mean_dev_lag, na.rm = TRUE), 
                                 ag_work          = mean(ag_work_lag, na.rm = TRUE),
                                 n_obs = n()) %>%
                       mutate(ag_work = ifelse(ag_work == 1, "Ag Worker", "Non-Ag Worker"))) + 
  geom_point(aes(x = norm_dev_prcp, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_prcp, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_prcp, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Precipitation - Deviation (Z-score, t-1)",
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17)) +
  theme(legend.position="bottom") +
  guides(shape=
           guide_legend(override.aes=
                          list(color=c("blue","red","black")))) +
  facet_wrap(~ag_work)

prcp_ow_plt +  ggtitle("Precipitation and Migration", 
                       subtitle = "Agricultural Worker")
```

```{r}
ggsave(paste0(dir$fig,"prec_dev_ag_work_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
prcp_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"prcp_dev_ag_work_plt_prest.png"), 
       width = 7, height = 4.5)
```


```{r}
tavg_m_dev = mean(mmp_com_weather$tavg_y_mean_dev_lag, na.rm = T)

tavg_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(ag_work_lag)) %>%
                       mutate(rank_tavg_dev = ntile(temp_avg_y_mean_dev_lag, 10)) %>%
                       group_by(rank_tavg_dev, ag_work_lag) %>% 
                       summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                                 M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                                 M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                                 norm_dev_tavg  = mean(temp_avg_y_mean_dev_lag, na.rm = TRUE), 
                                 ag_work          = mean(ag_work_lag, na.rm = TRUE),
                                 n_obs = n()) %>%
                       mutate(ag_work = ifelse(ag_work == 1, "Ag Worker",
                                               "Non-Ag Worker"))) + 
  geom_point(aes(x = norm_dev_tavg, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tavg, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tavg, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Avg Temperature - Deviation Historial (Z-score, t-1)", 
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
  theme(legend.position="bottom") +
  guides(shape=
           guide_legend(override.aes=
                          list(color=c("blue","red","black")))) +
  facet_wrap(~ag_work)

tavg_ow_plt +  
  ggtitle("Avg Temperature and Migration", 
          subtitle = "Agricultural Worker")
```

```{r}
ggsave(paste0(dir$fig,"tavg_dev_ag_work_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tavg_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tavg_dev_ag_work_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_m_dev = mean(mmp_com_weather$tmax_y_mean_dev_lag, na.rm = T)

tmax_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(ag_work_lag)) %>%
                       mutate(rank_tmax_dev = ntile(temp_max_y_mean_dev_lag, 10)) %>%
                       group_by(rank_tmax_dev, ag_work_lag) %>% 
                       summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                                 M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                                 M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                                 norm_dev_tmax  = mean(temp_max_y_mean_dev_lag, na.rm = TRUE), 
                                 ag_work        = mean(ag_work_lag, na.rm = TRUE),
                                 n_obs = n()) %>%
                       mutate(ag_work = 
                                ifelse(ag_work == 1, 
                                       "Ag Worker", "Non-Ag Worker"))) + 
  geom_point(aes(x = norm_dev_tmax, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tmax, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmax, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Max Temperature - Deviation (Z-score, t-1)", 
       y = "Migration (% of Population)") + 
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
  theme(legend.position="bottom") +
  guides(shape=
           guide_legend(override.aes=
                          list(color=c("blue","red","black")))) +
  facet_wrap(~ag_work)

tmax_ow_plt +
  ggtitle("Max Temperature and Migration", 
          subtitle = "Agricultural Worker")
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_ag_work_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_ag_work_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tmin_m_dev = mean(mmp_com_weather$tmin_y_mean_dev_lag, na.rm = T)

tmin_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(ag_work_lag)) %>%
                       mutate(rank_tmin_dev = ntile(temp_min_y_mean_dev_lag, 10)) %>%
                       group_by(rank_tmin_dev, ag_work_lag) %>% 
                       summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                                 M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                                 M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                                 norm_dev_tmin  = mean(temp_min_y_mean_dev_lag, na.rm = TRUE), 
                                 ag_work          = mean(ag_work_lag, na.rm = TRUE),
                                 n_obs = n()) %>%
                       mutate(ag_work = ifelse(ag_work == 1, 
                                               "Ag Worker", 
                                               "Non-Ag Worker")))  + 
  geom_point(aes(x = norm_dev_tmin, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") +
  geom_point(aes(x = norm_dev_tmin, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmin, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Min Temperature - Deviation (Z-score, t-1)", y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
  theme(legend.position="bottom") +
  guides(shape=
           guide_legend(override.aes=
                          list(color=c("blue","red","black")))) +
  facet_wrap(~ag_work)

tmin_ow_plt + 
  ggtitle("Min Temperature and Migration", 
          subtitle = "Agricultural Worker")
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_ag_work_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmin_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_ag_work_plt_prest.png"), 
       width = 7, height = 4.5)
```


## Land or Business owner

We also divide by land or business owner:
```{r}
mmp_com_weather = mmp_com_weather %>%
  arrange(id, year) %>%
  mutate(owner_lag = lag(owner))
```


```{r}
prec_m_dev = mean(mmp_com_weather$prec_y_mean_dev_lag, na.rm = T)

prcp_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(owner_lag)) %>%
         mutate(rank_prcp_dev = ntile(prec_y_mean_dev_lag, 10)) %>%
         group_by(rank_prcp_dev, owner_lag) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_prcp  = mean(prec_y_mean_dev_lag, na.rm = TRUE), 
                   owner          = mean(owner_lag, na.rm = TRUE),
                   n_obs = n()) %>%
         mutate(owner = ifelse(owner == 1, "Owner", "Non-Owner"))) + 
  geom_point(aes(x = norm_dev_prcp, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_prcp, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_prcp, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Precipitation - Deviation (Z-score, t-1)",
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17)) +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~owner)

prcp_ow_plt +  ggtitle("Precipitation and Migration", 
          subtitle = "Land or Bussiness Owner")
```

```{r}
ggsave(paste0(dir$fig,"prec_dev_owner_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
prcp_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"prcp_dev_owner_plt_prest.png"), 
       width = 7, height = 4.5)
```


```{r}
tavg_m_dev = mean(mmp_com_weather$tavg_y_mean_dev_lag, na.rm = T)

tavg_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(owner_lag)) %>%
         mutate(rank_tavg_dev = ntile(temp_avg_y_mean_dev_lag, 10)) %>%
         group_by(rank_tavg_dev, owner_lag) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tavg  = mean(temp_avg_y_mean_dev_lag, na.rm = TRUE), 
                   owner          = mean(owner_lag, na.rm = TRUE),
                   n_obs = n()) %>%
         mutate(owner = ifelse(owner == 1, "Owner", "Non-Owner"))) + 
  geom_point(aes(x = norm_dev_tavg, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tavg, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tavg, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Avg Temperature - Deviation Historial (Z-score, t-1)", 
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~owner)

tavg_ow_plt +  
  ggtitle("Avg Temperature and Migration", 
          subtitle = "Land or Business Owner")
```

```{r}
ggsave(paste0(dir$fig,"tavg_dev_owner_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tavg_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tavg_dev_owner_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_m_dev = mean(mmp_com_weather$tmax_y_mean_dev_lag, na.rm = T)

tmax_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(owner_lag)) %>%
         mutate(rank_tmax_dev = ntile(temp_max_y_mean_dev_lag, 10)) %>%
         group_by(rank_tmax_dev, owner_lag) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tmax  = mean(temp_max_y_mean_dev_lag, na.rm = TRUE), 
                   owner        = mean(owner_lag, na.rm = TRUE),
                   n_obs = n()) %>%
         mutate(owner = ifelse(owner == 1, "Owner", "Non-Owner"))) + 
  geom_point(aes(x = norm_dev_tmax, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tmax, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmax, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Max Temperature - Deviation (Z-score, t-1)", 
       y = "Migration (% of Population)") + 
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~owner)

tmax_ow_plt +
  ggtitle("Max Temperature and Migration", 
          subtitle = "Land or Business Owner")
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_owner_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_owner_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tmin_m_dev = mean(mmp_com_weather$tmin_y_mean_dev_lag, na.rm = T)

tmin_ow_plt = ggplot(mmp_com_weather %>% filter(!is.na(owner_lag)) %>%
         mutate(rank_tmin_dev = ntile(temp_min_y_mean_dev_lag, 10)) %>%
         group_by(rank_tmin_dev, owner_lag) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tmin  = mean(temp_min_y_mean_dev_lag, na.rm = TRUE), 
                   owner          = mean(owner_lag, na.rm = TRUE),
                   n_obs = n()) %>%
         mutate(owner = ifelse(owner == 1, "Owner", "Non-Owner")))  + 
  geom_point(aes(x = norm_dev_tmin, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") +
  geom_point(aes(x = norm_dev_tmin, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmin, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Min Temperature - Deviation (Z-score, t-1)", y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17))  +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~owner)

tmin_ow_plt + 
  ggtitle("Min Temperature and Migration", 
          subtitle = "Land or Business Owner")
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_owner_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmin_ow_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_owner_plt_prest.png"), 
       width = 7, height = 4.5)
```


## Age

Lastly, we divide the sample by age:
```{r}
mmp_com_age_plot = mmp_com_weather %>%
         mutate(rank_prcp_dev = ntile(prec_y_mean_dev_lag, 10),
                rank_tavg_dev = ntile(temp_avg_y_mean_dev_lag, 10),
                rank_tmax_dev = ntile(temp_max_y_mean_dev_lag, 10),
                rank_tmin_dev = ntile(temp_min_y_mean_dev_lag, 10))
```

```{r}
mmp_com_weather = mmp_com_weather %>%
  mutate(age_lag = age - 1,
         age_cat_lag = as.numeric(age_lag<42))

mmp_com_weather = mmp_com_weather %>% 
  mutate(M_U_young  = ifelse(age_cat_lag==1,M_UIL,NA), 
         M_U_old    = ifelse(age_cat_lag==0,M_UIL,NA))
```

```{r}
prcp_age_plt = ggplot(mmp_com_weather %>% filter(!is.na(age_cat_lag)) %>%
         mutate(rank_prcp_dev = ntile(prec_y_mean_dev_lag, 10)) %>%
         group_by(rank_prcp_dev, age_cat_lag) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_prcp  = mean(prec_y_mean_dev_lag, na.rm = TRUE), 
                   age_cat          = mean(age_cat_lag, na.rm = TRUE),
                   n_obs = n()) %>%
         mutate(age_cat = ifelse(age_cat == 1, "1. Age ≤ 41", 
                                 "2. Age > 41"))) + 
  geom_point(aes(x = norm_dev_prcp, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_prcp, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_prcp, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Precipitation - Deviation (Z-score, t-1)", 
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17)) +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~age_cat)

prcp_age_plt +  ggtitle("Precipitation and Migration", 
          subtitle = "Grouped by Age")
```

```{r}
ggsave(paste0(dir$fig,"prec_dev_age_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
prcp_age_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"prcp_dev_age_plt_prest.png"), 
       width = 7, height = 4.5)
```


```{r}
tavg_age_plt = ggplot(mmp_com_weather %>% filter(!is.na(age_cat_lag)) %>%
         mutate(rank_tavg_dev = ntile(temp_avg_y_mean_dev_lag, 10)) %>%
         group_by(rank_tavg_dev, age_cat_lag) %>% 
         summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                   M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                   M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                   norm_dev_tavg  = mean(temp_avg_y_mean_dev_lag, na.rm = TRUE), 
                   age_cat          = mean(age_cat_lag, na.rm = TRUE),
                   n_obs = n()) %>%
         mutate(age_cat = ifelse(age_cat == 1, "1. Age ≤ 41", 
                                 "2. Age > 41"))) + 
  geom_point(aes(x = norm_dev_tavg, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tavg, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tavg, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Avg Temperature - Deviation (Z-score, t-1)", 
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17)) +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~age_cat)

tavg_age_plt +  ggtitle("Avg Temperature and Migration", 
          subtitle = "Grouped by Age")
```

```{r}
ggsave(paste0(dir$fig,"tavg_dev_age_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tavg_age_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tavg_dev_age_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_age_plt = ggplot(mmp_com_weather %>% filter(!is.na(age_cat_lag)) %>%
                        mutate(rank_tmax_dev = ntile(temp_max_y_mean_dev_lag, 10)) %>%
                        group_by(rank_tmax_dev, age_cat_lag) %>% 
                        summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                                  M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                                  M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                                  norm_dev_tmax  = mean(temp_max_y_mean_dev_lag, na.rm = TRUE), 
                                  age_cat          = mean(age_cat_lag, na.rm = TRUE),
                                  n_obs = n()) %>%
                        mutate(age_cat = ifelse(age_cat == 1, "1. Age ≤ 41", 
                                                "2. Age > 41"))) + 
  geom_point(aes(x = norm_dev_tmax, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tmax, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmax, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Max Temperature - Deviation (Z-score, t-1)", 
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17)) +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~age_cat)

tmax_age_plt +  ggtitle("Max Temperature and Migration", 
                        subtitle = "Grouped by Age")
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_age_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmax_age_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmax_dev_age_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
tmin_age_plt = ggplot(mmp_com_weather %>% filter(!is.na(age_cat_lag)) %>%
                        mutate(rank_tmin_dev = ntile(temp_min_y_mean_dev_lag, 10)) %>%
                        group_by(rank_tmin_dev, age_cat_lag) %>% 
                        summarise(M_U_prop       = mean(M_U, na.rm = TRUE)*100, 
                                  M_UIL_prop     = mean(M_UIL, na.rm = TRUE)*100, 
                                  M_UL_prop      = mean(M_UL, na.rm = TRUE)*100, 
                                  norm_dev_tmin  = mean(temp_min_y_mean_dev_lag, na.rm = TRUE), 
                                  age_cat          = mean(age_cat_lag, na.rm = TRUE),
                                  n_obs = n()) %>%
                        mutate(age_cat = ifelse(age_cat == 1, "1. Age ≤ 41", 
                                                "2. Age > 41"))) + 
  geom_point(aes(x = norm_dev_tmin, y = M_U_prop,  shape = "Total"), size = 3,
             color = "black") + 
  geom_point(aes(x = norm_dev_tmin, y = M_UIL_prop,shape = "Illegal"), size = 3,
             color = "blue") +
  geom_point(aes(x = norm_dev_tmin, y = M_UL_prop, shape = "Legal"), size = 3,
             color = "red") + 
  labs(x = "Min Temperature - Deviation (Z-score, t-1)", 
       y = "Migration (% of Population)") +
  geom_vline(xintercept = 0) +
  scale_shape_manual(name = "", values = c("Total" = 15, 
                                           "Illegal" = 16, 
                                           "Legal" = 17)) +
  theme(legend.position="bottom") +
       guides(shape=
                guide_legend(override.aes=
                                   list(color=c("blue","red","black")))) +
  facet_wrap(~age_cat)

tmin_age_plt +  ggtitle("Min Temperature and Migration", 
                        subtitle = "Grouped by Age")
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_age_plt.png"), 
       width = 7, height = 4.5)
```

```{r}
tmin_age_plt + 
  theme(text = element_text(size = 14))
```

```{r}
ggsave(paste0(dir$fig,"tmin_dev_age_plt_prest.png"), 
       width = 7, height = 4.5)
```

```{r}
rm(list = ls(pattern = "plt"))
```


# Regressions

## Baseline

```{r}
mmp_com_weather %>% ungroup() %>%
  summarise(prop_movers    = mean(M_U, na.rm = T), 
            prop_il_movers = mean(M_UIL, na.rm = T), 
            prop_l_movers  = mean(M_UL, na.rm = T))
```


## Regressions

We regress the migration decision against the z-score of:

- Yearly (April-September) precipitations,
- Yearly (April-September) temperature,
- Yearly (April-September) maximum temperature,
- Yearly (April-September) minimum temperature.

### Agriculutral Worker
```{r}
mmp_com_weather = mmp_com_weather %>%
  mutate(M_U_ag  = ifelse(ag_work_lag==1,M_U,NA), 
         M_U_nag = ifelse(ag_work_lag==0,M_U,NA))
```


```{r}
formula = "M_U_ag ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_ag = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(ag_work_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_ag ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(ag_work_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_ag = c(reg_list_imm_ag, list(reg_round))
}
```


```{r}
formula = "M_U_nag ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_nag = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(ag_work_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_nag ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(ag_work_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_nag = c(reg_list_imm_nag, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_ag = "Migrant - Ag", 
                 M_U_nag = "Migrant - Non-Ag",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_nag[1:4], reg_list_imm_ag[1:4]),
       file = paste0(dir$results,"imm_ag_results_all.txt"), 
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_nag[1:4], reg_list_imm_ag[1:4]))
```

#### Illegal Migration
```{r}
mmp_com_weather = mmp_com_weather %>%
  mutate(M_U_ag  = ifelse(ag_work_lag==1,M_UIL,NA), 
         M_U_nag = ifelse(ag_work_lag==0,M_UIL,NA))
```


```{r}
formula = "M_U_ag ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_ag = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(ag_work_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_ag ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(ag_work_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_ag = c(reg_list_imm_ag, list(reg_round))
}
```


```{r}
formula = "M_U_nag ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_nag = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(ag_work_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_nag ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(ag_work_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_nag = c(reg_list_imm_nag, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_ag = "Illegal Migrant - Ag", 
                 M_U_nag = "Illegal Migrant - Non-Ag",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_nag[1:4], reg_list_imm_ag[1:4]),
       file = paste0(dir$results,"imm_ag_results.txt"), 
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_nag[1:4], reg_list_imm_ag[1:4]))
```

#### Legal Migration
```{r}
mmp_com_weather = mmp_com_weather %>%
  mutate(M_U_ag  = ifelse(ag_work_lag==1,M_UL,NA), 
         M_U_nag = ifelse(ag_work_lag==0,M_UL,NA))
```


```{r}
formula = "M_U_ag ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_ag = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(ag_work_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_ag ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(ag_work_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_ag = c(reg_list_imm_ag, list(reg_round))
}
```


```{r}
formula = "M_U_nag ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_nag = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(ag_work_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_nag ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(ag_work_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_nag = c(reg_list_imm_nag, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_ag = "Illegal Migrant - Ag", 
                 M_U_nag = "Illegal Migrant - Non-Ag",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_nag[1:4], reg_list_imm_ag[1:4]),
       file = paste0(dir$results,"imm_ag_results_l.txt"), 
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_nag[1:4], reg_list_imm_ag[1:4]))
```

### Land and Business Owners
```{r}
mmp_com_weather = mmp_com_weather %>%
  mutate(M_U_ow  = ifelse(owner_lag==1,M_U,NA), 
         M_U_now = ifelse(owner_lag==0,M_U,NA))
```


```{r}
formula = "M_U_ow ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_ow = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(owner_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_ow ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(owner_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_ow = c(reg_list_imm_ow, list(reg_round))
}
```


```{r}
formula = "M_U_now ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_now = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(owner_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_now ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(owner_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_now = c(reg_list_imm_now, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_ow = "Owner Migrant", M_U_now = "Non-Owner Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_now[1:4], reg_list_imm_ow[1:4]),
       file = paste0(dir$results,"imm_ow_results_all.txt"), 
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_now[1:4], reg_list_imm_ow[1:4]))
```

#### Illegal Migration
```{r}
mmp_com_weather = mmp_com_weather %>%
  mutate(M_U_ow  = ifelse(owner_lag==1,M_UIL,NA), 
         M_U_now = ifelse(owner_lag==0,M_UIL,NA))
```


```{r}
formula = "M_U_ow ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_ow = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(owner_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_ow ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(owner_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_ow = c(reg_list_imm_ow, list(reg_round))
}
```


```{r}
formula = "M_U_now ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_now = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(owner_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_now ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(owner_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_now = c(reg_list_imm_now, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_ow = "Owner Illegal Migrant", M_U_now = "Non-Owner Illegal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_now[1:4], reg_list_imm_ow[1:4]),
       file = paste0(dir$results,"imm_ow_results.txt"), 
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_now[1:4], reg_list_imm_ow[1:4]))
```

#### Llegal Migration
```{r}
mmp_com_weather = mmp_com_weather %>%
  mutate(M_U_ow  = ifelse(owner_lag==1,M_UL,NA), 
         M_U_now = ifelse(owner_lag==0,M_UL,NA))
```


```{r}
formula = "M_U_ow ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_ow = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(owner_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_ow ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(owner_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_ow = c(reg_list_imm_ow, list(reg_round))
}
```


```{r}
formula = "M_U_now ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_now = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(owner_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_now ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(owner_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_now = c(reg_list_imm_now, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_ow = "Owner Legal Migrant",
                 M_U_now = "Non-Owner Legal Migrant",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_now[1:4], reg_list_imm_ow[1:4]),
       file = paste0(dir$results,"imm_ow_results_l.txt"), 
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_now[1:4], reg_list_imm_ow[1:4]))
```


### Age

```{r}
mmp_com_weather = mmp_com_weather %>% 
  mutate(M_U_young  = ifelse(age_cat_lag==1,M_U,NA), 
         M_U_old    = ifelse(age_cat_lag==0,M_U,NA))
```

```{r}
formula = "M_U_young ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_young = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(age_cat_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_young ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(age_cat_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_young = c(reg_list_imm_young, list(reg_round))
}
```


```{r}
formula = "M_U_old ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_old = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(age_cat_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_old ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(age_cat_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_old = c(reg_list_imm_old, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_young = "Migrant $\\leq 41$", 
                 M_U_old = "Migrant $> 41$",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_young[1:4],reg_list_imm_old[1:4]),
       file = paste0(dir$results,"imm_age_results_all.txt"),
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_young[1:4],reg_list_imm_old[1:4]))
```

#### Illegal Migration

```{r}
mmp_com_weather = mmp_com_weather %>% 
  mutate(M_U_young  = ifelse(age_cat_lag==1,M_UIL,NA), 
         M_U_old    = ifelse(age_cat_lag==0,M_UIL,NA))
```


```{r}
formula = "M_U_young ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_young = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(age_cat_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_young ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(age_cat_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_young = c(reg_list_imm_young, list(reg_round))
}
```


```{r}
formula = "M_U_old ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_old = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(age_cat_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_old ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(age_cat_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_old = c(reg_list_imm_old, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_young = "Illegal Migrant $\\leq 41$", 
                 M_U_old = "Illegal Migrant $> 41$",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_young[1:4],reg_list_imm_old[1:4]),
       file = paste0(dir$results,"imm_age_results.txt"),
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_young[1:4],reg_list_imm_old[1:4]))
```

#### Legal Migration

```{r}
mmp_com_weather = mmp_com_weather %>% 
  mutate(M_U_young  = ifelse(age_cat_lag==1,M_UL,NA), 
         M_U_old    = ifelse(age_cat_lag==0,M_UL,NA))
```

```{r}
formula = "M_U_young ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_young = list(feols(as.formula(formula), 
                             data = mmp_com_weather %>% filter(age_cat_lag == 1), se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_young ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(age_cat_lag==1), se = 'cluster', cluster = "commun")
  
  reg_list_imm_young = c(reg_list_imm_young, list(reg_round))
}
```


```{r}
formula = "M_U_old ~ prec_y_mean_dev_lag | id + year"
reg_list_imm_old = list(feols(as.formula(formula), 
                              data = mmp_com_weather %>% filter(age_cat_lag==0), 
                              se = 'cluster', cluster = "commun"))

for (i in c("temp_avg", "temp_max", "temp_min")) {
  formula = paste0("M_U_old ~ ",i,"_y_mean_dev_lag | id + year")
  
  reg_round = feols(as.formula(formula), 
                    data = mmp_com_weather %>% filter(age_cat_lag==0), se = 'cluster', cluster = "commun")
  
  reg_list_imm_old = c(reg_list_imm_old, list(reg_round))
}
```


```{r}
setFixest_dict(c(M_U_young = "Illegal Migrant $\\leq 41$", 
                 M_U_old = "Illegal Migrant $> 41$",
                 prec_y_mean_dev_lag     = "Dev Precipitation (Z-score, t-1)", 
                 temp_avg_y_mean_dev_lag = "Dev Avg Temp (Z-score, t-1)",
                 temp_max_y_mean_dev_lag = "Dev Max Temp (Z-score, t-1)",
                 temp_min_y_mean_dev_lag = "Dev Min Temp (Z-score, t-1)"))

etable(c(reg_list_imm_young[1:4],reg_list_imm_old[1:4]),
       file = paste0(dir$results,"imm_age_results_l.txt"),
       fitstat=c('n', 'ar2'), replace = TRUE)

etable(c(reg_list_imm_young[1:4],reg_list_imm_old[1:4]))
```